\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

%----------HYPERLINK SETUP----------
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
}

%----------FONT OPTIONS----------
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins to fit single page perfectly
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Harish R} \\ \vspace{3pt}
    
    \small 
    \href{tel:+918807639930}{\underline{+91 88076 39930}} $|$ 
    \href{mailto:harish.r2023ai-ds@sece.ac.in}{\underline{harish.r2023ai-ds@sece.ac.in}} $|$ 
    \href{https://linkedin.com/in/harish-r-12372b28b/}{\underline{LinkedIn}} $|$
    \href{https://github.com/Harish24-10-2005}{\underline{GitHub}} $|$
    \href{https://harishravikumar.netlify.app/}{\underline{Portfolio}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sri Eshwar College of Engineering}{Coimbatore, India}
      {B.Tech in Artificial Intelligence and Data Science; CGPA: 8.34}{2023 -- 2027 (Expected)}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Operating Systems, AI, CN, DBMS, OOP, Big Data.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++ (C++17, STL, Multi-threading), Python, Java, SQL, C.} \\
     \textbf{Systems \& Low-Level}{: Memory Management, Distributed Systems, System Design (HLD/LLD), Operating Systems.} \\
     \textbf{AI \& GenAI}{: LLM Fine-tuning (QLoRA, Unsloth), Quantization, AI Agents, RAG, LangChain, MCP, Vector DBs.} \\
     \textbf{Big Data Engineering}{: Apache Kafka, Spark (PySpark), Hadoop, Airflow, NiFi, Microservices.} \\
     \textbf{DevOps \& Tools}{: Docker, Git/GitHub, FastAPI (Async), MongoDB, MySQL, Postman, n8n, LangSmith.}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {INEUDATA}{}
      {Data Engineering Intern}{2025}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable ETL pipelines leveraging \textbf{Apache Kafka}, \textbf{PySpark}, \textbf{Hadoop}, and \textbf{Airflow}.}
        \resumeItem{Successfully automated \textbf{40\%} of manual data workflows and visualized large-scale datasets for actionable insights.}
        \resumeItem{Integrated processed data streams with SQL-based storage to power real-time analytics dashboards.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Key Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{\href{https://www.linkedin.com/posts/sketch-mentor_edtech-aiforgood-digitaleducation-activity-7351124054105280512-LyIL/}{\underline{Sketch Mentor: AI-Powered Mathematical Reasoning Engine}}} $|$ \emph{Python, QLoRA, Unsloth}}{}
          \resumeItemListStart
            \resumeItem{\textbf{Model Optimization:} Fine-tuned Qwen2.5-Coder-7B using \textbf{QLoRA} and 4-bit quantization, boosting Manim code accuracy from $<$30\% to \textbf{95\%} while significantly reducing training time and memory usage.}
            \resumeItem{\textbf{Orchestration:} Architected a multi-agent pipeline with adaptive retry logic to interpret, solve, and verify complex problems.}
            \resumeItem{\textbf{Visuals:} Developed a verified stepwise visual solution generator using the Manim engine.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\href{https://github.com/Harish24-10-2005/Big-Data}{\underline{Real-Time Streaming Analytics Platform}}} $|$ \emph{Kafka, Spark, Hadoop, Airflow, MCP}}{}
          \resumeItemListStart
            \resumeItem{\textbf{Distributed Architecture:} Deployed a Kafka streaming pipeline with 4 multi-producers and 2 topic-based consumers.}
            \resumeItem{\textbf{Hybrid Processing:} Integrated batch (Hadoop/Spark) and stream processing for scalable analytics on OTT datasets.}
            \resumeItem{\textbf{AI Interface:} Developed an agentic dashboard with \textbf{LangChain} and \textbf{MCP}, enabling NL-to-SQL queries for real-time visualization.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\href{https://github.com/Harish24-10-2005/Horix-Yt}{\underline{HorixYt: AI Agentic Video Automation}}} $|$ \emph{Python, FastAPI (Async), Gemini LLM}}{}
          \resumeItemListStart
            \resumeItem{\textbf{High Throughput:} Scaled throughput \textbf{3–5x} using a FastAPI-based async architecture and parallel processing.}
            \resumeItem{\textbf{Automation:} Built a multi-agent system converting prompts to videos, automating 7 production stages and reducing manual effort by $\sim$\textbf{95\%}.}
            \resumeItem{\textbf{Resilience:} Integrated Gemini LLM, SQLite, and Docker for a fault-tolerant generation pipeline.}
          \resumeItemListEnd
          
       \resumeProjectHeading
          {\textbf{\href{https://github.com/Harish24-10-2005/Horix-Ai-Backend-}{\underline{Horix AI: Autonomous Tooling Infrastructure}}} $|$ \emph{Node.js, Python, Asyncio, MCP}}{}
          \resumeItemListStart
            \resumeItem{Built a platform for the autonomous discovery and configuration of MCP tools, enabling dynamic capability expansion.}
            \resumeItem{Designed resilient orchestration with automated GitHub discovery and AI-assisted run-config generation.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS & CODING METRICS-----------
\section{Achievements \& Coding Metrics}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\href{https://leetcode.com/u/harishravikumar2005/}{\underline{LeetCode}}}{: Max Rating \textbf{1,755} (Top 9\% Global) $|$ \textbf{700+} Problems Solved (Strong DSA foundation).} \\
     \textbf{\href{https://www.codechef.com/users/harishr2005}{\underline{CodeChef}}}{: Max Rating 1,464 (2 Star) $|$ Global Rank: 23,461.} \\
     \textbf{Hackathons}{: \textbf{Winner (1st Place)} - Creatathon (Solo Hackathon) \& Python Project Expo.} \\
     \textbf{Competitions}{: \textbf{Winner (1st Place)} - Electra Code Debugging Challenge \& Code Fiesta Coding Contest.}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Advanced Machine Learning Algorithms (Stanford) $|$ Data Structures \& Algorithms Mastery (Udemy) \\
     Programming in C (NPTEL - Focus on Pointers) $|$ Programming in Python for Data Science (IBM)
    }}
 \end{itemize}

\end{document}